Reactor like TGE model

### 2019-07-04 AYSS-2019/article/ZelenyyAYSS-2019.tex
Fix adress

\author{Mikhail Zelenyi} % Write as First name Surname
\email[Corresponding author: ]{mihail.zelenyy@phystech.edu}
\affiliation{
Moscow Institute of Physics and Technology}
\affiliation{%
Institute for Nuclear Research of RAS
}%
\affiliation{
Space Research Institute of RAS
}
\author{Alexander Nozik}%
\email{altavir@gmail.com}
\author{Egor Stadnichuk}
\email{egrstadnichuk@yandex.ru}
\affiliation{
Moscow Institute of Physics and Technology}
\affiliation{%
Institute for Nuclear Research of RAS
}%

>>>>

\author{Mikhail Zelenyi} % Write as First name Surname
\email[Corresponding author: ]{mihail.zelenyy@phystech.edu}
\affiliation{
Moscow Institute of Physics and Technology, 1 "A" Kerchenskaya st., Moscow, 117303, Russian Federation}
\affiliation{%
Institute for Nuclear Research of RAS, prospekt 60-letiya Oktyabrya 7a, Moscow, Russia, 117312
}%
\affiliation{
Space Research Institute of RAS,  84/32 Profsoyuznaya Str, Moscow, Russia, 117997 
}
\author{Alexander Nozik}%
\email{altavir@gmail.com}
\author{Egor Stadnichuk}
\email{egrstadnichuk@yandex.ru}
\affiliation{
Moscow Institute of Physics and Technology, 1 "A" Kerchenskaya st., Moscow, 117303, Russian Federation}
\affiliation{%
Institute for Nuclear Research of RAS, prospekt 60-letiya Oktyabrya 7a, Moscow, Russia, 117312
}%
